МНОЖЕСТВА ТОЧЕК С ЦЕЛОЧИСЛЕННЫМИ РАССТОЯНИЯМИ НА ПЛОСКОСТИ И В ЕВКЛИДОВОМ ПРОСТРАНСТВЕ

### 2018-09-23 vmmsh-2018/AvdeevNN_09.cp1251.tex
[vmmsh] Meta

 \Adress{\textsc{Авдеев Николай Николаевич}\\
 Воронежский госуниверситет\\
 Россия, Воронеж, Университетская пл., 1\\
 avdeev@math.vsu.ru}

 \Adress{\textsc{Семенов Евгений Михайлович}\\
 Воронежский госуниверситет\\
 Россия, Воронеж, Университетская пл., 1\\
 E-mail}

>>>>

 \Adress{\textsc{Авдеев Николай Николаевич}\\
 Воронежский госуниверситет\\
 Россия, 394036, Воронеж, Университетская пл., 1\\
 avdeev@math.vsu.ru}

 \Adress{\textsc{Семенов Евгений Михайлович}\\
 Воронежский госуниверситет\\
 Россия, 394036, Воронеж, Университетская пл., 1\\
 nadezhka\_ssm@geophys.vsu.ru}
